Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex

\documentclass[twocolumn, a4paper,10pt]{article}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.0cm, right=2.0cm,
columnsep=0.8cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{boxedminipage}
\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[font=it]{caption}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{tabularx}
%-----------------------------SET SKIP SPACES -------------------------------------------------------------------
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{3pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
%\renewcommand{\baselinestretch}{0.7}
% FOR enumerates
\setlist{itemsep=-0.1cm,topsep=0.1cm,labelsep=0.3cm}
\setenumerate{leftmargin=*}
\setcounter{secnumdepth}{-1}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulation and visualisation of mitigation and adaption strategy pathways for urban districts
%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Simulation and visualization framework for decision making of climate mitigation  																								% Line 1
%%% Please keep the \vspace{4pt} between lines in the title
\vspace{4pt}
and adaptation strategies in new and existing urban development} 																																% Line 2 
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
% Justin McCarty$^1$, Adam Rysanek$^1$
\\ 																				% Line 4
% $^1$The University of British Columbia, Vancouver, Canada
\\ 																																                                                            	% Line 5
% $^2$Institution 2, City 2, Country 2
\\ 																																                                                                % Line 6
% comment the lines below and add \phantom{} lines as needed to reach a total of 10 lines
% \textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}
\\ 			 			  	                                                    % Line 7
% \textit{(leave blank up to line 10 - remove line numbering from final version)}
\\ 														                    	% Line 8
\phantom{Line 9}} 																																								            	% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														                                                            % Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

It is also of particular importance when developing infrastructure or buildings to consider the impact of a changing climate. Adaptation is prevalent in designing buildings in proximity to rising seas, with strategies ranging from hard measures such as levies and dams to soft measures such as wetland restoration \citep{mimura_adaptation_nodate}. Evidence is pointing to the need to consider other impacts, such as overheating risk due to generally warmer days, nights with less cooling capacity, and more intense heat waves \citep{lomas_overheating_2017,rysanek_forecasting_2021}. Measuring adaptation is a contentious field, as what defines successful adaptation is not as simple to calculate as net carbon emissions \citep{noble_adaptation_2014}. \citet{brooks_tracking_2011} suggests several general criteria by which successful adaptation can be assessed: feasibility, efficacy/effectiveness, efficiency, acceptability/legitimacy, equity, and sustainability. The same authors also discuss the concept of \textit{Maladaptation}, or the inadvertent increase in vulnerability to climate change as a result of development, which has equal importance to adaptation planning of buildings. For all criteria though, measures begin with assessing vulnerability of a subject to a stressor or collection of stressors. In the case of coastal development, a building's adaptive capacity and success can be measured by its vulnerability to increasingly intense sea level rise and storm surge. In the case of this study the stressor is heat gain and the vulnerability of a building to overheating.

@@

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1]{figures/budget_macc.eps}
    \caption{Illustrative MACC made assuming a budget of \$11 million in net cost was permitted for any plotted strategy-set.}
    \label{fig:MACC_budget}
\end{figure}

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1]{figures/threshold_macc.eps}
    \caption{Illustrative MACC made assuming an emissions reduction threshold of 80\% was necessary for any plotted strategy-set.}
    \label{fig:MACC_threshold}
\end{figure}

@@

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}. Figure \ref{fig:MACC_true_noDH_waterfall} describes how each strategy contributes to the overall decrease in emissions. The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction. This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity. The majority of the abatement can be attributed to the heat pump strategy, removing natural gas from the fuel mix, while the other strategies can be said to lending to adaptability. This point about the fuel mix will be returned to more in the discussion, but raises that question about how to affordably meet zero-carbon targets after fuel-switching has been achieved. This scenario only achieves 67\% emissions reduction over the baseline by 2080.

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1]{figures/true_macc_noDH_waterfall.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_noDH_waterfall}
\end{figure}

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=0.8]{figures/true_macc_noDH.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_noDH}
\end{figure}

A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario. Figure \ref{fig:MACC_true_DH_waterfall} describes how each measure contributes to overall emissions reduction. The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.

\begin{figure*}[hbpt]
    \centering
    \includegraphics[scale=0.8]{figures/true_macc_dh.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_DH}
\end{figure*}

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1]{figures/true_macc_DH_waterfall.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_DH_waterfall}
\end{figure}

@@

%---------------------------------------------------------------------------------------
This document is a summary of various documents from previous Building Simulation Conferences.
%here starts the references
\bibliographystyle{BS2021}
\bibliography{bs2021_ref}
\newpage
\onecolumn
Please \textbf{do not} include this disclaimer in your paper.  You will be required to accept these conditions when you  submit your paper via the web site.

\begin{figure*}[ht]
\centering

\end{figure*}

\end{document}

>>>>

\documentclass[twocolumn, a4paper,10pt]{article}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.0cm, right=2.0cm,
columnsep=0.8cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{boxedminipage}
\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[font=it]{caption}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
%-----------------------------SET SKIP SPACES -------------------------------------------------------------------
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{3pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
%\renewcommand{\baselinestretch}{0.7}
% FOR enumerates
\setlist{itemsep=-0.1cm,topsep=0.1cm,labelsep=0.3cm}
\setenumerate{leftmargin=*}
\setcounter{secnumdepth}{-1}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulation and visualisation of mitigation and adaption strategy pathways for urban districts
%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Simulation and visualization framework for decision making of climate mitigation  																								% Line 1
%%% Please keep the \vspace{4pt} between lines in the title
\vspace{4pt}
and adaptation strategies in new and existing urban development} 																																% Line 2 
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
% Justin McCarty$^1$, Adam Rysanek$^1$
\\ 																				% Line 4
% $^1$The University of British Columbia, Vancouver, Canada
\\ 																																                                                            	% Line 5
% $^2$Institution 2, City 2, Country 2
\\ 																																                                                                % Line 6
% comment the lines below and add \phantom{} lines as needed to reach a total of 10 lines
% \textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}
\\ 			 			  	                                                    % Line 7
% \textit{(leave blank up to line 10 - remove line numbering from final version)}
\\ 														                    	% Line 8
\phantom{Line 9}} 																																								            	% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														                                                            % Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

It is also of particular importance when developing infrastructure or buildings to consider the impact of a changing climate. Adaptation is prevalent in designing buildings in proximity to rising seas, with strategies ranging from hard measures such as levies and dams to soft measures such as wetland restoration \citep{pachauri_climate_2015}. Evidence is pointing to the need to consider other impacts, such as overheating risk due to generally warmer days, nights with less cooling capacity, and more intense heat waves \citep{lomas_overheating_2017,rysanek_forecasting_2021}. Measuring adaptation is a contentious field, as what defines successful adaptation is not as simple to calculate as net carbon emissions \citep{pachauri_climate_2015}. \citet{brooks_tracking_2011} suggests several general criteria by which successful adaptation can be assessed: feasibility, efficacy/effectiveness, efficiency, acceptability/legitimacy, equity, and sustainability. The same authors also discuss the concept of \textit{Maladaptation}, or the inadvertent increase in vulnerability to climate change as a result of development, which has equal importance to adaptation planning of buildings. For all criteria though, measures begin with assessing vulnerability of a subject to a stressor or collection of stressors. In the case of coastal development, a building's adaptive capacity and success can be measured by its vulnerability to increasingly intense sea level rise and storm surge. In the case of this study the stressor is heat gain and the vulnerability of a building to overheating.

@@

\begin{figure*}
\centering
\begin{minipage}[b]{.45\textwidth}
    \hspace*{-1.05cm}\includegraphics[scale=1.0]{figures/budget_macc.eps}
    \caption{Illustrative MACC made assuming a budget of \$11 million in net cost was permitted for any plotted strategy-set.}
    \label{fig:MACC_budget}
\end{minipage}\qquad
\begin{minipage}[b]{.45\textwidth}
    \hspace*{-.4cm}\includegraphics[scale=1.0]{figures/threshold_macc.eps}
    \caption{Illustrative MACC made assuming an emissions reduction threshold of 80\% was necessary for any plotted strategy-set.}
    \label{fig:MACC_threshold}
\end{minipage}
\end{figure*}

@@

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}. Figure \ref{fig:MACC_true_noDH} describes how each strategy contributes to the overall decrease in emissions. The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction. This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity. The majority of the abatement can be attributed to the heat pump strategy, removing natural gas from the fuel mix, while the other strategies can be said to lending to adaptability. This point about the fuel mix will be returned to more in the discussion, but raises that question about how to affordably meet zero-carbon targets after fuel-switching has been achieved. This scenario only achieves 67\% emissions reduction over the baseline by 2080.

% \begin{figure}[hbpt]
%     \centering
%     \includegraphics[scale=1]{figures/true_macc_noDH_waterfall.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_noDH_waterfall}
% \end{figure}

% \begin{figure}[hbpt]
%     \centering
%     \includegraphics[scale=0.8]{figures/true_macc_noDH.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_noDH}
% \end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[scale=0.8]{figures/true_macc_noDH_waterfall_comb.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_noDH}
\end{figure}

A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario. Figure \ref{fig:MACC_true_DH} describes how each measure contributes to overall emissions reduction. The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.

% \begin{figure*}[hbpt]
%     \centering
%     \includegraphics[scale=0.8]{figures/true_macc_dh.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_DH}
% \end{figure*}

% \begin{figure}[hbpt]
%     \centering
%     \includegraphics[scale=1]{figures/true_macc_DH_waterfall.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_DH_waterfall}
% \end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[scale=0.8]{figures/true_macc_DH_waterfall_comb.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_DH}
\end{figure}

@@

%---------------------------------------------------------------------------------------
This document is a summary of various documents from previous Building Simulation Conferences.
%here starts the references
\bibliographystyle{BS2021}
\bibliography{bs2021_ref}
% \newpage
% \onecolumn
% Please \textbf{do not} include this disclaimer in your paper.  You will be required to accept these conditions when you  submit your paper via the web site.
\end{document}
